Reproducibility in Plant Pathology

### 2018-04-07 README.rmd
Update README
Include Docker file information

The package has a number of dependencies on other R packages, and programs
outside of R. These are listed at the bottom of this README. Installing these can be time-consuming and complicated, so we've done two things to simplify access to the compendium. First is the `packrat/` directory, which contains the
source code for all the packages we depend on. If all works well, these will be
installed on your computer when you open `Reproducibility_in_Plant_Pathology.Rproj` in RStudio.

<!--- Second is our Docker image that includes all the necessary software, code and data to run our analysis. The Docker image may give a quicker entry point to the project, and is more self-contained, so might save some fiddling with installing things.

@@

    docker run -dp 8787:8787 openplantpathology/Reproducibility_in_Plant_Pathology

@@

Once logged in, use the Files pane (bottom right) to navigate to `/` (the root directory), then open the folder for this project, and open the `.Rproj` file for this project. Once that's open, you'll see the `analysis/paper` directory in the Files pane where you can find the R markdown document, and knit them to produce the results in the paper. More information about using RStudio in Docker is avaiable at the [Rocker](https://github.com/rocker-org) [wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.

We developed and tested the package on this Docker container, so this is the only platform that We're confident it works on, and so recommend to anyone wanting to use this package to generate the vignette, etc. 
--->

>>>>

The package has a number of dependencies on other R packages, and programs
outside of R. These are listed at the bottom of this README. Installing these can be time-consuming and complicated, so we've provided a Docker image that includes all the necessary software, code and data to run our analysis. The Docker image may give a quicker entry point to the project, and is more self-contained, so might save some fiddling with installing things.

@@

    docker run -dp 8787:8787 adamhsparks/reproducibility_in_plant_pathology

@@

Once logged in, use the Files pane (bottom right) to navigate to `Reproduciblity_in_Plant_Pathology` folder for this project, and open the `.Rproj` file for this project. Once that's open, you'll see the `analysis/paper` directory in the Files pane where you can find the R markdown document, and knit them to produce the results in the paper. More information about using RStudio in Docker is available at the [Rocker](https://github.com/rocker-org) [wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.

We developed and tested the package on this Docker container, so this is the only platform that we're confident it works on, and so recommend to anyone wanting to use this package to generate the vignette, etc.
